Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{ Funded by DARPA Cyber Assured Systems Engineering (CASE) contract HR00111890001. }

### 2021-05-07 paper/system.tex
Add summary of semantics

>>>>

The notation $(\lval \mapsto \mathit{slice}) \bullet \theta$ denotes the addition of binding $\lval \mapsto \mathit{slice}$ to $\theta$. Create an eval function for \konst{eq}-statement. Map it to the list of statements. Create a similar function for the guarantees with its map that fails if invariance does not hold. Define the language of the specification using the contiguity notation. Need to munge all the types into a single $\tau$, but the gist is the language is any finite stream possible that conform to the input specification are the result of the eq-statements, and are invariant. The set is prefix closed (trace theory).
